Case for Support

### 2021-11-16 application/caseForSupport.tex
Added \description in section Potential for economic and societal impact

\section{Potential for economic and societal impact}
\textbf{Understanding the brain and behaviour.} Systems neuroscientists aim to uncover how adaptive behaviour arises
from computation in neural circuits in different brain regions. Extending the Bonsai ecosystem will facilitate new types of experiment that causally connect neural circuits with elemental behavioural processes. Long-term, this research will help identify the missing links between circuit dysfunction and behavioural deficits in neurological or mental health disorders, and will pave the way for the development of new neural circuit biomarkers and therapies. The Bonsai ecosystem will also enable the experimental testing of emerging theories of brain function and learning, and thus contribute to the neuro-inspired machine learning algorithms that fuel intelligent technologies, increasingly important in our society.
The enhanced Bonsai platform will also support purely behavioural experiments, in which the animals' posture, body parts or location are tracked in real-time, allowing investigation of environmental variables or captivity on their behaviour, especially important for assessment of animal welfare.

\textbf{Improve reproducibility in behavioural and brain sciences.} Lack of reproducible results slows down scientific progress and incurs personal and economic costs to scientists and funders.  In neuroscience,  many behavioural and neural animal studies have been to be difficult to reproduce, and experiments are rarely replicated across laboratories. By creating a resource that standardises and enables reproducible experimental design/control, as well as analysis of neural and behavioural data, the Bonsai ecosystem will allow multiple laboratories to implement and align experimental and analytical protocols as closely as possible.

\textbf{Improve efficiency of research.} Most neuroscience laboratories worldwide develop custom, unique solutions to their experimental control and analysis needs. Some laboratories also lack the technical know-how to either develop their own software for experimental hardware control or write software for the state-of-the-art analysis of rich neural and behavioural data, increasingly reliant on latest machine learning algorithms. The proposed upgrading of the open-source and community empowered Bonsai ecosystem with a toolbox of online and offline analytical tools, that can dovetail with closed-loop experimental requirements, will (i) allow the deployment of such tools into laboratories that lack the expertise, (ii) reduce the need to reinvent the same tools in multiple labs (cost/time efficiency) and (iii) concomitantly streamline and standardise the experimental data processing streams in systems neuroscience.

>>>>

\section{Potential for economic and societal impact}

\begin{description}

    \item[Understanding the brain and behaviour] Systems neuroscientists aim to
        uncover how adaptive behaviour arises from computation in neural
        circuits in different brain regions. Extending the Bonsai ecosystem
        will facilitate new types of experiment that causally connect neural
        circuits with elemental behavioural processes. Long-term, this research
        will help identify the missing links between circuit dysfunction and
        behavioural deficits in neurological or mental health disorders, and
        will pave the way for the development of new neural circuit biomarkers
        and therapies. The Bonsai ecosystem will also enable the experimental
        testing of emerging theories of brain function and learning, and thus
        contribute to the neuro-inspired machine learning algorithms that fuel
        intelligent technologies, increasingly important in our society.  The
        enhanced Bonsai platform will also support purely behavioural
        experiments, in which the animals' posture, body parts or location are
        tracked in real-time, allowing investigation of environmental variables
        or captivity on their behaviour, especially important for assessment of
        animal welfare.

    \item[Improve reproducibility in behavioural and brain sciences] Lack of
        reproducible results slows down scientific progress and incurs personal
        and economic costs to scientists and funders.  In neuroscience,  many
        behavioural and neural animal studies have been to be difficult to
        reproduce, and experiments are rarely replicated across laboratories.
        By creating a resource that standardises and enables reproducible
        experimental design/control, as well as analysis of neural and
        behavioural data, the Bonsai ecosystem will allow multiple laboratories
        to implement and align experimental and analytical protocols as closely
        as possible.

    \item[Improve efficiency of research] Most neuroscience laboratories
        worldwide develop custom, unique solutions to their experimental
        control and analysis needs. Some laboratories also lack the technical
        know-how to either develop their own software for experimental hardware
        control or write software for the state-of-the-art analysis of rich
        neural and behavioural data, increasingly reliant on latest machine
        learning algorithms. The proposed upgrading of the open-source and
        community empowered Bonsai ecosystem with a toolbox of online and
        offline analytical tools, that can dovetail with closed-loop
        experimental requirements, will (i) allow the deployment of such tools
        into laboratories that lack the expertise, (ii) reduce the need to
        reinvent the same tools in multiple labs (cost/time efficiency) and
        (iii) concomitantly streamline and standardise the experimental data
        processing streams in systems neuroscience.

\end{description}
